---
title: "Compare the fit of multiple polynomal regressions"
author: "David Kaiser"
date: "2018-09-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("compare_model_fits.R")
```

## Description

This function fits multiple polynomal regressions to x and y data. The user supplies the highest degree of polynomal that should be included and all polynomals from one to that degree will be calculated. A summary table will be output. ANOVA is performed on consecutive polynomal regressions (e.g. cubic vs quadratic fit) to indicate which increase in polynomal degree still produces a significant reduction in residual sum of squares.

## Arguments

+ *x* - a vector of x values
+ *y* - a vector of y values
+ *degrees* - numeric value for the highest degree polynomal
+ *plot* - logical, should the results be plotted? defaults to TRUE

## Result

A data frame giving for each polynomal  R², the adjusted R², f-statistic value and the p-value of the regression, as well as the Residual Sum of Squares and the ANOVA p-value.
A plot showing the data and the different fits (if plot = TRUE).

## Example

```{r example, echo = TRUE}
x <- seq(1,20,length.out = 20)
y <- x^seq(1,2,length.out = 20)
compare_model_fits(x, y, degrees = 3)
```
