---
title: "Compare the fit of multiple polynomal regressions"
author: "David Kaiser"
date: "2018-03-07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("compare_model_fits.R")
```

## Description

This function fits multiple polynomal regressions to x and y data. The user supplies the highest degree of polynomal that should be included and all polynomals from one to that degree will be calculated. A summary table and a printed result will be output.

## Arguments

+ *x* - a vector of x values
+ *y* - a vector of y values
+ *degrees* - numeric value for the highest degree polynomal
+ *plot* - logical, should the results be plotted? defaults to TRUE

## Result

A data frame giving for each polynomal the Residual Sum of Squares, R², the adjusted R² and the p-value of the regression
A printed sentence showing which polynomal best fits the data.
A plot showing the data and the different fits (if plot = TRUE).

## Example

```{r example, echo = TRUE}
x <- seq(1,20,length.out = 20)
y <- x^seq(1,2,length.out = 20)
compare_model_fits(x, y, degrees = 3)
```
